%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,10pt]{article}

%***************************************************************************************************%
% Variables Section %
%***************************************************************************************************%

%***************************************************************************************************%
% Header Section %
%***************************************************************************************************%
% define packages used
\usepackage{CV}

%need to set this in here (this doesn't look good on regular docs, so it isn't in the sty)
\titlespacing*{\section}{0pt}{3pt}{3pt}

\setlength{\tabcolsep}{0pt}
\newcommand{\reitem}[2]{
  \begin{tabular}[t]{l}
    #2
  \end{tabular}
\hfill
\begin{tabular}[t]{r}
  #1
\end{tabular}
}


\newcommand{\sidebyside}[2]{
  %\fbox{
  \begin{minipage}[t]{.75\textwidth}
    \raggedright{}
    #2
  \end{minipage}
  %}
  %\hfill
  %\fbox{
  \hspace{.01\textwidth}
    \begin{minipage}[t]{.205\textwidth}
    \raggedleft
    #1
  \end{minipage}
%}
}

\newcommand{\quadItem}[4]{\reitem{\emph{#1}\\#2}{\textbf{#3}\\#4}}
\newcommand{\award}[3]{\textbf{#2}, #1\\#3}
\newcommand{\paper}[3]{#1. #2 #3}
\newcommand{\desc}[1]{\hspace*{.5em}#1}
\newcommand{\trio}[3]{\sidebyside{#3}{\textbf{#1}. #2}}

%***************************************************************************************************%
% Header Section %
%***************************************************************************************************%

%% Header Information
% name
\title{andrew quinn}
\author{Assistant Professor\\Computer Science \& Engineering\\ University of California, Santa Cruz}
% address
\def \addr {Office \#365, Engineering \#2\\1156 High Street\\Santa Cruz, CA 95064}
% phone number
\def \phone {1.630.453.1899}
% email
\def \email {\href{mailto:aquinn1@ucsc.edu}{aquinn1@ucsc.edu}}
\def \website {\href{https://arquinn.github.io}{arquinn.github.io}}


\begin{document}
\maketitle
\setlength\parindent{0pt}
\setlength{\parskip}{3pt}


\begin{tabular}[t]{l}
  \addr
\end{tabular}
\hfill
\begin{tabular}[t]{r}
  Phone: \phone\\
  Email: \email\\
  Web: \website
\end{tabular}

%\vspace{0.1in}}

%***************************************************************************************************%
% Introduction Section %
%***************************************************************************************************%
%\section{Research Interests}
%My research aims to make it easier for developers to build correct and
%efficient software systems.  I propose techniques and systems that
%change the way developers debug their software, build tools that
%automatically find bugs, and perform taxonomies of the bugs we see in
%software that use emerging hardware platforms.  My work builds on
%insights from across systems, programming languages, software
%engineering, and computer architecture.

%***************************************************************************************************%
% Education Section %
%***************************************************************************************************%
\section{Education}
\quadItem{Ann Arbor, MI}{(Sep 2015--Dec 2021)}{University of
  Michigan}{Ph.D., Computer Science and Engineering\\Thesis:
  Data-Centric Execution Inspection}
\quadItem{Ann Arbor, MI}{(Sep 2015--May 2017)}{University of Michigan}{M.S.,
  Computer Science and Engineering}
\quadItem{Granville, OH}{(Aug 2010--May 2014)}{Denison University}{B.S.,
  Computer Science and B.A., Mathematics\\ Honors: \textit{summa cum
    laude}, Phi Beta Kappa, Deans List}


%***************************************************************************************************%
% Honors Section %
%***************************************************************************************************%
\section{Awards \& Funding}
\begin{smenumerate}
\item \trio{ISSTA Distinguished Artifact Award}{``GPUHarbor''}{(2023)}
\item \trio{ASPLOS Distinguished Paper Award}{``MC Mutants''}{(2023)}
\item \trio{ASPLOS Distinguished Artifact Award}{``MC Mutants''}{(2023)}
\item \trio{Meta}{Finalist for Silent Data Corruptions at Scale}{(2022)}
\item \trio{Google Gift}{Co-author of ``Towards Fuzzing for Production Bugs''.}{(2021)}
\item \trio{IEEE Micro Top Pick Honorable Mention}{``Agamotto''}{(2021)}
%\item \trio{OSDI Student Travel Grant}{}{(2018)}
%\item \trio{SOSP Student Travel Grant}{}{(2017)}
  %\item \trio{OSDI Student Travel Grant}{}{(2016)}
\item \trio{Microsoft Research Fellowship}{}{(2017)}
\item \trio{National Science Foundation Graduate Student Research
  Fellowship}{}{(2017)}
\item \trio{John L. Gilpatrick Mathematics Award, Denison University}{Awarded to
  the most outstanding senior major in the Math and CS department}{(2014)}
\item \trio{Ted Barclay Top Five Student Athlete, Denison University}{Awarded to
  the top five student athletes at Denison University based on GPA.}{(2014)}
\end{smenumerate}

%\section{Funding}
%\begin{smenumerate}

%\end{smenumerate}
%**************************************************************************************************
% Publications
%***************************************************************************************************
\section{Peer-reviewed Conference Publications}
\begin{smenumerate}
\item \paper{Reese Levine, Mingun Cho, Devon McKee, \textbf{Andrew Quinn}, and
  Tyler Sorensen}{\emph{GPUHarbor: Testing GPU Memory Consistency At Large
  (Experience Paper)}.  In Proceedings of the Thirty-Second ACM SIGSOFT
  International Symposium on Software Testing and Analysis (ISSTA). July
  2023.}{Acceptance Rate: $117/406=28.8\%$}\
  \item \paper{Reese Levine, Tianhao Guo, Mingun Cho, Allen Baker, Raph Levien,
    David Neto, \textbf{Andrew Quinn}, and Tyler Sorensen}{\emph{MC Mutants:
    Evaluating and Improving Testing for Memory Consistency Specifications}. In
    Proceedings of the Twenty-Eighth International Conference on Architectural
    Support for Programming Languages and Operating Systems (ASPLOS). March
    2023.}{Acceptance Rate: $126/600=21\%$}
  \item \paper{Gefei Zuo, Jiacheng Ma, \textbf{Andrew Quinn}, and Baris
    Kasikci}{\emph{Vidi: Record Replay for Reconfigurable Hardware}. In
    Proceedings of the Twenty-Eighth International Conference on Architectural
    Support for Programming Languages and Operating Systems (ASPLOS). March
    2023.}{Acceptance Rate: $126/600=21\%$}
  \item \paper{\textbf{Andrew Quinn}, Michael Cafarella, Jason Flinn, and Baris
    Kasikci}{\emph{Debugging the OmniTable Way}.  In Proceedings of the 2022
    USENIX Symposium on Operating Systems Design and Implementation (OSDI).
    July 2022.}{Acceptance Rate: $49/253=19.4\%$}
  \item \paper{Jiacheng Ma, Gefei Zuo, Kevin Loughlin, Haoyang Zhang,
    \textbf{Andrew Quinn}, and Baris Kasikci}{\emph{Debugging in the Brave New
    World of Reconfigurable Hardware}. In Proceedings of the Twenty-Seventh
    International Conference on Architectural Support for Programming Languages
    and Operating Systems (ASPLOS). February 2022.}{Acceptance Rate:
    $80/397=20.1\%$}
  \item \paper{Gefei Zuo, Jiacheng Ma, \textbf{Andrew Quinn}, Pramod
    Bhatotia, Pedro Fonseca, and Baris Kasikci}{\emph{Reproducing
    Production Failures with Execution Reconstruction}. In Proceedings
    of the 42\textsuperscript{nd} ACM SIGPLAN Conference on
    Programming Language Design and Implementation. June
    2021.}{Acceptance Rate: $87/320=27.2\%$}
  \item \paper{Ian Neal, \textbf{Andrew Quinn}, and Baris
    Kasikci}{\emph{Hippocrates: Healing Persistent Memory Bugs Without
    Doing Any Harm}. In the Proceedings of the Twenty-Sixth
    International Conference on Architectural Support for Programming
    Languages and Operating Systems (ASPLOS). April 2021.}{Acceptance
    Rate: $75/398=18.8\%$}
  \item \paper{Ian Neal, Ben Reeves, Ben Stoler, \textbf{Andrew Quinn}, Youngjin Kwon,
    Simon Peter and Baris Kasikci}{\emph{Agamotto: How Persistent is your
    Persistent Memory Application?}.  In Proceedings of the 2020 USENIX
    Symposium on Operating Systems Design and Implementation (OSDI).  November
    2020.}{Acceptance Rate: $70/398=17.6\%$}
  \item \paper{\textbf{Andrew Quinn}, Jason Flinn, and Michael Cafarella}{
    \emph{Sledgehammer: Cluster-fueled Debugging}.  In Proceedings of the 2018
    USENIX Symposium on Operating Systems Design and Implementation (OSDI).
    October 2018.}{Acceptance Rate: $47/264 = 17.8\%$}
  \item \paper{\textbf{Andrew Quinn}, David Devecsery, Peter M. Chen and Jason
    Flinn}{\emph{JetStream: Cluster-scale Parallelization of Information
    Flow Queries}.  In Proceedings of the 2016 USENIX Symposium on
    Operating Systems Design and Implementation (OSDI). November
    2016.}{Acceptance Rate: $47/267=17.6\%$}
\end{smenumerate}

\section{Peer-reviewed Workshop Publications}
\begin{smenumerate}
  \item \paper{Matt Furlong, \textbf{Andrew Quinn}, and Jason Flinn}
    {\emph{The case for Determinism on the Edge}.  In 2nd USENIX
      Workshop on Hot Topics in Edge Computing (HotEdge).  July
      2019.}{Acceptance Rate: $22/39=56\%$}
  \item \paper{\textbf{Andrew Quinn}, Michael Cafarella, and Jason
    Flinn}{\emph{You can't debug what you can't see: Expanding
    observability with the OmniTable}. In Proceedings of the Workshop
    on Hot Topics in Operating Systems (HotOS).  May 2019.}{Acceptance
    Rate: $30/125=24\%$}
\end{smenumerate}


%**************************************************************************************************
% Presentations
%***************************************************************************************************
\section{Talks}
\begin{smenumerate}
\item\trio{Data-Centric Debugging or: How I learned to stop worrying
  and use `Big-Data' Techniques to Diagnose Software
  Bugs}{Berkeley/Stanford/UCSC Cloud Workshop}{(May 2022)}
\item\trio{You can't debug what you can't see: Expanding Observability
  with the OmniTable}{Workshop on Hot Topics in Operating Systems
  (HotOS)}{(May 2019)}
\item\trio{Sledgehammer: Cluster-fueled Debugging}{USENIX Symposium on
  Operating Systems Design and Implementation (OSDI)}{(Oct 2018)}
\item\trio{JetStream: Cluster-Scale Parallelization of Information
  Flow Queries}{USENIX Symposium on Operating Systems Design and
  Implementation (OSDI)}{(Nov 2016)}
\item\trio{Power Management for Malleable Job Scheduling}{Denison
  University department of Math and Computer Science FaST talk}{(Apr
  2014)}
\end{smenumerate}


%**************************************************************************************************
% Professional Service
%***************************************************************************************************
\section{Service}
%\subsubsection*{Professional}
\begin{smenumerate}
%\item\trio{External Review Committee Member}{Architectural Support for
%  Programming Languages and Operating Systems (ASPLOS)}{(2022)}
\item\trio{ASPLOS}{External Review Committee Member}{(2021), (2022)}
\item\trio{Eurosys}{Program Committee Member}{(2022)}
\item\trio{PLDI Student Research Competition}{Program Committee Member}{(2022)}
\item\trio{SOSP}{Mentorship chair}{(2021)}
\item\trio{SOSP}{AMA Moderator}{(2021)}
\item\trio{Discover Engineering}{University of Michigan, Ann Arbor, MI}{(Aug 2019)}
\item\trio{Techie Club}{Georgian Heights Elementary, Columbus, OH}{(Aug 2014--Aug 2015)}
\item\trio{A Call to College}{Newark Elementary Schools, Newark, OH}{(Sep 2012--Dec 2013)}
\end{smenumerate}

%***************************************************************************************************
% Outreach
%***************************************************************************************************%
%\subsubsection*{Outreach}
%\begin{smenumerate}
%\end{smenumerate}


%**************************************************************************************************
% Teaching
%***************************************************************************************************

\section{Teaching}
\begin{smenumerate}
\item Fall 2022, Fall 2023. UC Santa Cruz. CSE 231---Advanced Operating Systems
\item Spring 2022. UC Santa Cruz. CSE 130---Introduction to Computer Systems
\end{smenumerate}

%**************************************************************************************************
% Experience
%***************************************************************************************************
\section{Professional Experience}
\begin{smenumerate}
\item\trio{Assistant Professor}{ University of California, Santa Cruz, Santa Cruz, CA.}{(Jul 2021--Present)}
\item\trio{Graduate Student}{Advisor: Dr.\ Jason Flinn and Dr.\ Baris Kasikci,
  University of Michigan, Ann Arbor, MI}{(Sep 2015--Sep 2021)}
\item\trio{Research Intern}{Mentor: Dr.\ Suman Nath, Microsoft Corp.,
  Redmond, WA}{(May 2017--Aug 2017)}
\item\trio{Software Development Engineer}{International Business Machines (IBM),
  Dublin, OH}{(Jun 2014--Aug 2015)}
%\item\trio{Research Assistant in Online Algorithms}{Mentor: Dr.\ Jessen Havill,
%  Denison University, Granville, OH}{(Aug 2013--May 2014)\\(May 2012--Aug 2012)}
%\item\trio{Software Development Engineering Intern}{International Business
%  Machines (IBM), Dublin, OH}{(May 2013--Aug 2013)}
\end{smenumerate}

\end{document}

